%\chapter*{ABSTRACT}
\begin{center}
{\bf ABSTRACT}\\[36pt]
\end{center}
\addcontentsline{toc}{chapter}{ABSTRACT}
{\baselineskip=2.0\baselineskip

This study focuses on the development of SUBAY: A Multi-Camera Detection System for Customer Tracking, aimed at monitoring customer movement and behavior within a retail setting. The system integrates YOLOv10 for detection, DeepSORT for tracking, and Omni-Scale Network (OSNet) for cross-camera re-identification. Detection testing across four camera views achieves an average precision of 100\%, a recall of 90.95\%, and an F1-score of 95.26\%. Customer re-identification using OSNet reaches an F1-score of 72.17\%, supporting identity continuity in crowded and occluded environments. Tracking accuracy is validated with an average bounding box overlap of 91.9\% and a 6.71-pixel difference from manual annotations. The system accurately counts 259 unique customers and calculates behavioral metrics such as visit frequency and dwell time. Zone B logged the most foot traffic with 102 entries recorded. A web-based analytics dashboard visualizes customer flow through interactive heat maps and charts, generating automated insights for store optimization. Functional testing with a local store owner in Cagayan de Oro, Philippines, results in 100\% success across all system components. A System Usability Scale (SUS) score of 87.5 reflects high user satisfaction. SUBAY demonstrates practical applicability in providing data-driven insights for retail layout planning and marketing strategies.

}
\bigskip
\parbox{\textwidth}{
	\textbf{Keywords:} \textit{Multi-Camera Object Detection, Multi-Camera Object Tracking, Customer Behavior Analytics, Computer Vision, YOLOv10, DeepSORT, Omni-Scale Feature Learning, Person Re-Identification (Re-ID), Retail Analytics.}
}

