%\chapter*{ACKNOWLEDGMENT}
\clearpage
\begin{center}
	{\bf ACKNOWLEDGMENT}\\[24pt]
\end{center}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENT}
\pagestyle{fancy} % Ensures following pages also have bottom center page number
{\baselineskip=1.5\baselineskip

We would like to express our gratitude to the individuals and institutions that, in some way, significantly contributed to the completion of this study.

First and foremost, we extend our most profound appreciation to our research adviser, \textbf{\textit{Engr. Jodie Rey D. Fernandez}}, for his unwavering support, expert guidance, and meticulous attention to detail. His encouragement and insightful feedback have been instrumental in shaping the direction and quality of our work. Without his patience and commitment, this study would not have reached its full potential.

We are also sincerely grateful to the members of our panel, \textbf{\textit{Engr. Rodesita S. Estenzo}}, \textbf{\textit{Engr. Sprinztsie Maye T. Garrucha}}, \textbf{\textit{Engr. Kristine Mae P. Dunque}}, and \textbf{\textit{Mr. Matthew Maulion}} for their generous contributions of time, thoughtful insights, and constructive critiques. Their expertise and dedication greatly enhanced the depth and clarity of our research. We also thank the \textbf{\textit{Department of Computer Engineering faculty and staff}} for their continuous support and encouragement.

Furthermore, we thank the \textbf{\textit{Center for Artificial Intelligence (CAI)}}, particularly \textbf{\textit{Engr. Harry Dale Lim}} for his support in setting up and maintaining the High Performance Computing Server. His contributions facilitated efficient model training and data analysis, significantly enhancing the technical quality of our system.

To the management and staff of \textbf{\textit{FashionLane Gift Shop}}, we express our profound thanks for their cooperation and for granting us access to their store. Their trust and openness made it possible for us to carry out this research in a real-world setting, and their assistance was vital to the success of this project.

We are equally thankful to our \textbf{\textit{families}}, \textbf{\textit{friends}}, and \textbf{\textit{loved ones}} for their boundless support, patience, and understanding. Their moral and financial support, along with their belief in our potential, inspired us to persevere through every challenge.

We sincerely appreciate those whose contributions may not have been individually mentioned but who offered support, encouragement, or prayers throughout this journey.

Above all, to our \textbf{\textit{Almighty God}}, whose unconditional love infinitely transcends all human comprehensions, provides us with good health, divine protection and bountiful blessings.

}