%\chapter*{ACKNOWLEDGMENT}
\begin{center}
	{\bf DEDICATION}\\[24pt]
\end{center}

\addcontentsline{toc}{chapter}{DEDICATION}
{\baselineskip=1.5\baselineskip
	
This thesis is a labor of love, perseverance, and collaboration. Behind every milestone reached and challenge overcome were the unwavering pillars of support who made this journey possible. As we present this work, we offer gratitude to those who have shaped and inspired us throughout this endeavor.
	
\textbf{\textit{Xyrus}} would like to dedicate this thesis to his parents, \textbf{\textit{Regie and Cristina}}, for their unwavering love, support, and sacrifices throughout his academic journey. Their constant encouragement and belief in his potential have been the foundation of his achievements. This work reflects his dedication and is a token of his deepest gratitude.

He also dedicates this work to his siblings, \textbf{\textit{Rex}} and \textbf{\textit{Lara}}, as a testament that dreams can be achieved through perseverance, dedication, and hard work. May this serve as an example and inspiration to always strive for their beliefs.

\textbf{\textit{Precious}} offers this thesis to her parents, \textbf{\textit{Allan}} and \textbf{\textit{Margie}}, whose prayers and unwavering belief in her fueled her determination. She also dedicates this to her younger siblings, \textbf{\textit{Selin}} and \textbf{\textit{Aboy}}, as a reminder that dreams are worth pursuing.

\textbf{\textit{Venz}} also extends his dedication to his mother, \textbf{\textit{Venice}}, grandmother, \textbf{\textit{Tessie}}, and his tita \textbf{\textit{Daisy}}, whose love, guidance, and enduring support have been his source of strength throughout this journey. Their sacrifices, encouragement, and unwavering belief in him have made every achievement possible. This thesis stands as a tribute to their profound influence on his life and success.

Lastly, \textbf{\textit{Rezzelle}} dedicates this thesis to her beloved parents, \textbf{\textit{Jocelyn}} and \textbf{\textit{Romeo}}, whose unwavering support, encouragement, and sacrifices have been instrumental throughout her academic journey. Their guidance has been the foundation of her perseverance and success.

She also expresses heartfelt gratitude to her younger brother, \textbf{\textit{Mekko}}, for being a constant source of emotional support and motivation; his encouragement served as a light during the most challenging times.

Finally, she extends sincere appreciation to her \textbf{\textit{siblings}}, \textbf{\textit{relatives}}, and \textbf{\textit{friends}} for their steadfast support, both financial and emotional. Their belief in her has played a vital role in helping her reach this critical milestone.

This study is also dedicated to the \textbf{\textit{management}} and \textbf{\textit{staff}} of \textbf{\textit{FashionLane Gift Shop}}, whose openness and support were vital to our research. We extend our deepest gratitude to all who helped us along the way, \textbf{\textit{friends}}, \textbf{\textit{mentors}}, and \textbf{\textit{peers}}. Your contributions have not gone unnoticed. Above all, we thank \textbf{\textit{Almighty God}} for His guidance, grace, and strength that sustained us from beginning to end.

}